---
title: "In Raw Form"
author: "Kent Russell"
date: "February 1, 2018"
output:
  html_document:
    theme: null
    mathjax: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE}
library(remiotic)
spi <- spiotic(
  # lines expected to be an array of arrays
  #  for now do it the really ugly way
  data = list(
    list(
      group = "A",
      coordinates = lapply(0:10, function(x) list(x=x, y=runif(1)))
    )
  ),
  frame = "SparkXYFrame",
  props = list(
    shape = "lines",
    xAccessor = "x",
    yAccessor = "y",
    xExtent = c(0, 10),
    yExtent = c(0, 1),
    lineStyle = list(stroke = "black")
  ),
  width = 100
)
```

`remiotic` will bring the power of Semiotic to R,`r spi`
and hopefully the R user won't have to know JavaScript to use it.  The lazy way to build the bridge is to not document or validate and force the user to pass a list of list of lists to make their graph.  Since this is the first version and merely a proof-of-concept, this lazy approach is what I have done.  Let's see if it works.  Since this is a Rmarkdown document, if charts appear, then we prove part of the concept.

## Install

This is raw, alpha, and will change dramatically and rapidly, so you have been warned.  To install, use `devtools::install_bitbucket`.  Yep, bitbucket to keep it sneaky.

```{r eval = FALSE}
devtools::install_github("timelyportfolio/remiotic")
```

## Points

So now to the list of lists that I promised that hopefully will go away one day.  We'll intentionally use common data from R to prove data from R and charts from JavaScript.

```{r}
library(remiotic)

remiotic(
  data = mtcars,
  frame = "XYFrame",
  props = list(
    shape = "points",
    xAccessor = "wt",
    yAccessor = "hp",
    pointStyle = list(fill = "black")
  ),
  width = 300,
  height = 200
)
```

Let's pass a bigger list to see what happens.

```{r}
remiotic(
  data = mtcars,
  props = list(
    title = "mtcars from R with Semiotic",
    shape = "points",
    xAccessor = "mpg",
    xExtent = range(mtcars$mpg),
    yAccessor = "hp",
    yExent = range(mtcars$hp),
    pointStyle = list(
      fill = "red",
      stroke = "blue",
      strokeWidth = 5,
      opacity = 0.5
    ),
    axes = list(
      list(orient = "left", label = "Miles per Gallon (mpg)"),
      list(orient = "bottom", label = "Horsepower (hp)")
    ),
    margin = list(
      top = 40,
      right = 20,
      bottom = 60,
      left = 70
    ),
    annotations = list(
      list(type = "x", label = "mpg > 21 is good", mpg = 21, color = "red", dy = 50)
    )
  ),
  width = 400,
  height = 400
)
```

## Lines

```{r}

remiotic(
  # lines expected to be an array of arrays
  #  for now do it the really ugly way
  #  but should be able to fix this fairly easily
  data = list(
    list(
      group = "A",
      coordinates = lapply(0:10, function(x) list(x=x, y=runif(1)))
    )
  ),
  frame = "XYFrame",
  props = list(
    shape = "lines",
    xAccessor = "x",
    yAccessor = "y",
    xExtent = c(0, 10),
    yExtent = c(0, 1),
    lineStyle = list(stroke = "#629"),
    margin = list(
      top = 20,
      right = 40,
      bottom = 50,
      left = 50
    ),
    axes = list(
      list(orient = "left"),
      list(orient = "bottom")
    )
  ),
  width = "100%"
)

```

## Discussion of API Options

One way we might handle the API would be to start with a `frame` and then add shapes.  Here is how that might look with `XYFrame` and `points`.

```{r}
library(remiotic)
library(magrittr)

XYFrame(
  data = iris,
  xAccessor = "Petal.Length",
  xExtent = c(0, max(iris$Petal.Length)),
  yAccessor = "Petal.Width",
  yExtent = c(0, max(iris$Petal.Width)),
  title = "Semiotic Using Frames API",
  margin = list(top = 60, right = 20, bottom = 40, left = 50),
  height = 400,
  width = "100%"
) %>%
  rem_points() %>%
  rem_axes(orient = "bottom") %>%
  rem_axes(orient = "left")

```
